Looking for CDI Bias

### 2021-07-02 01-preliminary.Rmd
figuring out multigroup

d_demo <- d_demo %>% filter(production!=0) %>%
  arrange(data_id)

@@

sex_group = d_demo$sex

mg1 <- multipleGroup(dat, model = 1, group = sex_group, verbose = FALSE) 
mg2 <- multipleGroup(dat, model = 1, group = sex_group, 
                     invariance = 'slopes', verbose = FALSE)

>>>>

d_demo <- d_demo %>% 
  filter(production!=0, !is.na(sex)) %>% # can't fit children not producing words, or with NA sex in group model
  arrange(data_id)

@@

sex_group = as.character(d_demo$sex)

# mg1 <- multipleGroup(d_mat, model = 1, group = sex_group, verbose = FALSE) 
# Error: Multiple Group model will not be identified without proper constraints (groups contain missing data patterns where item responses have been completely omitted or, alternatively, the number of categories within each group is not equal to the total number of categories)
mg2 <- multipleGroup(d_mat, model = 1, group = sex_group, 
                     invariance = 'slopes', verbose = FALSE)
